A first implementation of Section 3 of ``Bla Parabolic''

### 2019-08-01 Python/time/readme.tex
added an ODE solver test

\usepackage{amssymb}
\usepackage{geometry}
\usepackage{commath}
\usepackage{dsfont}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{todonotes}
\geometry{margin=2.5cm}
%\setlength{\parindent}{0pt}

@@

@@

In any case, right now,

>>>>

\usepackage{amssymb}
\usepackage{bm}
\usepackage{geometry}
\usepackage{commath}
\usepackage{dsfont}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{todonotes}
\geometry{margin=2.5cm}
%\setlength{\parindent}{0pt}

@@

\subsection{Some fun: solving an ODE}
I used the three-point basis on a uniform grid to solve some ODEs, in order
to test the (hopefully fast) application of the multiscale matrices inside an
iterative linear solver. I didn't completely succed, however.

My original goal was to solve $-u'' = f, u(0) = u(1) = 0$ using Galerkin on
both the singlescale and multiscale basis. See \texttt{ode\_test.py}. In
singlescale, it works perfectly and produces nice results (run the code). In
multiscale however, I was unable to find the right subset of indices to impose
a boundary condition on, in order to get results that were nice. I think I may
have solved a different equation entirely, maybe Rob will have some more ideas
(very likely, this idea was senseless). Still, I was able to solve the
``zeroth-order'' ODE $u = f$ by using the multiscale mass matrix. This is nice
enough.

@@

In any case, right now, we are (more or less) able to evaluate a time-operator
in linear time. If we now use the \texttt{space-fem.py} code to convert a
multiscale operator to a singlescale operator, we could in principe use a more
optimized library for the singlescale space operations (or, in the mean time,
use our own). With both of those elements in place, it is not a far leap to
implementing Theorem 4.1 from the document, although I do not quite understand
how to compute $\bm \Sigma$ and $\bm \Theta$.

I am unsure if the current framework is suitable for spacetime computations
as-is, because I was mostly concerned with building a working time-framework.
It is very well possible that to efficiently compute the fibers and other
spacetime index set stuff, we need different data structures altogether.
